Procurements of the Canadian Government, Runaway Military Contracts

### 2024-11-29 paper/paper.qmd
added more TODO

df <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
aggregated_df <- (here::here("data/analysis_data/top_ten_suppliers.csv"))
models <- read_csv(here::here("models/buyer_models.rds"))
```

@@

aggregated_df <- aggregated_df %>%
  left_join(top_ten %>% select(word, supplier_name), by = "word")

@@

# 10. Transform `processed_supplier` into a Character Column for CSV
df <- df %>%
  mutate(
    processed_supplier = sapply(processed_supplier, function(x) {
      if(length(x) > 0) {
        paste(x, collapse = " ")
      } else {
        ""  # Represent empty lists as empty strings
      }
    })
  )
```

@@

>>>>

df <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
aggregated_df <- read_csv(here::here("data/analysis_data/top_ten_suppliers.csv"))
models <- read_csv(here::here("models/buyer_models.rds"))

View(df)
```

@@

#TODO Fix colors and supplier names

@@

@@

TODO add spending by selected buyers graph
